A Comparison of Parallel Graph Processing Implementations

### 2017-05-16 papers/publication/paper-pollard.tex
Updated BFS strong scaling title, misc fixes.

\begin{table}
	\caption{Graphalytics: tabulated sample run times (seconds) with 32 threads. Just one run per experiment is performed. Below the table is an excerpt from the GraphMat log file.}
		\label{tab:graphalytics-realworld}
	\vspace{-10pt}
	\begin{center}
	% cit-Patents: (3 774 768 vertices, 16 518 948 edges)
	% dota-league (61 170 vertices, 50 870 313 edges)
	\begin{tabular}{l|c|c|c|c|c|c}
	%% BN: Commented out because it's redundant with the caption
	%\multicolumn{5}{l}{\large{\emph{Graphalytics}}}  \\
	GraphBIG & BFS  & CDLP  &   LCC   &  PR &  SSSP & WCC \\ \hline
	cit-Patents & 0.8 & 11.8 & 15.5  &  4.5 & N/A  & 1.3 \\
	dota-league & 1.1 & 3.9 & 1073.7 &  2.6 & \textbf{3.0} & 1.0 \\
	\multicolumn{1}{l}{}\\
	PowerGraph & BFS  & CDLP  &   LCC   &  PR &  SSSP & WCC \\ \hline
	cit-Patents & 13.8 & 30.1 & 23.9 & 18.8 & N/A & 22.1 \\
	dota-league & 25.6 & 31.2 & 458.1 & 26.7 & 28.9 & 22.9 \\
	% graph500-22 43.0 s 55.6 s 299.8 s 46.4 s N/A    40.5 s
	\multicolumn{1}{l}{}\\
	GraphMat & BFS  & CDLP  &   LCC   &  PR &  SSSP & WCC \\ \hline
	cit-Patents & 7.8 & 20.6 & 11.2 &  8.4 & N/A &  7.0 \\
	dota-league & 2.2 & 19.7 & 150.1 & 2.8 & \textbf{3.8} & 3.1\\ \hline
	\end{tabular}
	\end{center}
	%\vspace{12pt}
\noindent Timing results (for GraphMat SSSP on dota-league)
	\begin{itemize}
		\item Finished file read of dota-league. time: 0.9495
		\item load graph: 3.48167 sec
		\item initialize engine: 3.60012e-05 sec
		\item run algorithm: 0.168526 sec
		\item print output: 0.105846 sec
		\item deinitialize engine: 6.00815e-05 sec
	\end{itemize}
\end{table}

@@

These plots show generally poor scaling for this size problem, a challenge facing most parallel graph algorithms. 
\todo[inline]{If time permits, replace with a larger graph to show scaling.}
In addition, $2^{20}$ vertices is a relatively ``small'' graph resulting for by today's standards and thus library designers focus on scalability for larger graphs. Another limitation may be the ability for OpenMP to efficiently handle such a large number of threads per machine. GCC version 4.8.5 supports OpenMP version 3.1 but the most recent release of OpenMP is 4.5.

>>>>

\begin{table}
	\caption{Graphalytics: tabulated sample run times (seconds) with 32 threads. Just one run per experiment is performed. Below the table is an excerpt from the GraphMat log file.}
		\label{tab:graphalytics-realworld}
	\vspace{-10pt}
	\begin{center}
	% cit-Patents: (3 774 768 vertices, 16 518 948 edges)
	% dota-league (61 170 vertices, 50 870 313 edges)
	\begin{tabular}{l|c|c|c|c|c|c}
	%% BN: Commented out because it's redundant with the caption
	%\multicolumn{5}{l}{\large{\emph{Graphalytics}}}  \\
	GraphBIG & BFS  & CDLP  &   LCC   &  PR &  SSSP & WCC \\ \hline
	cit-Patents & 0.8 & 11.8 & 15.5  &  4.5 & N/A  & 1.3 \\
	dota-league & 1.1 & 3.9 & 1073.7 &  2.6 & \textbf{3.0} & 1.0 \\
	\multicolumn{1}{l}{}\\
	PowerGraph & BFS  & CDLP  &   LCC   &  PR &  SSSP & WCC \\ \hline
	cit-Patents & 13.8 & 30.1 & 23.9 & 18.8 & N/A & 22.1 \\
	dota-league & 25.6 & 31.2 & 458.1 & 26.7 & 28.9 & 22.9 \\
	% graph500-22 43.0 s 55.6 s 299.8 s 46.4 s N/A    40.5 s
	\multicolumn{1}{l}{}\\
	GraphMat & BFS  & CDLP  &   LCC   &  PR &  SSSP & WCC \\ \hline
	% This was with 64 threads
	%cit-Patents & 7.8 & 20.6 & 11.2 &  8.4 & N/A &  7.0 \\
	%dota-league & 2.2 & 19.7 & 150.1 & 2.8 & \textbf{3.8} & 3.1\\ \hline
	cit-Patents 8.3 & 21.7 & 11.4 & 9.1 & N/A & 7.8 \\
	dota-league 3.8 & 19.7 & 236.4 & 3.8 & 7.4 & 3.9 \\
	\end{tabular}
	\end{center}
	%\vspace{12pt}
\noindent Timing results (for GraphMat SSSP on dota-league)
	\begin{itemize}
		\item Finished file read of dota-league. time: 0.9495
		\item load graph: 3.48167 sec
		\item initialize engine: 3.60012e-05 sec
		\item run algorithm: 0.168526 sec
		\item print output: 0.105846 sec
		\item deinitialize engine: 6.00815e-05 sec
	\end{itemize}
\end{table}

@@

These plots show generally poor scaling for this size problem, a challenge facing most parallel graph algorithms. 
\todo[inline]{If time permits, replace with a larger graph to show scaling.}
In addition, $2^{20}$ vertices is a relatively small graph by today's standards and thus library designers focus on scalability for larger graphs. Another limitation may be the ability for OpenMP to efficiently handle such a large number of threads per machine. GCC version 4.8.5 supports OpenMP version 3.1 but the most recent release of OpenMP is 4.5.
